Stats

### 2022-08-09 stats/analysis.Rmd
save last state before dropping vali section

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse) # data handling etc.
library(viridis) # col scales, plotting...
library(ggpubr)
library(ggridges)
library(ggthemes)
library(tidyboot) # for bootstrap CIs
library(brms) # modeling
library(splithalfr) # reliability 
library(tidybayes) # for stat_halfeye
library(ggdist)

@@

```{r age_hedge_model}
mDataAgeHedge <- vali %>% 
  filter(studyversion == "hedge" & sample == "kids") %>% 
  mutate(
    # scaled (centered around mean, SD = 1, i.e., z-transformed)
    age = scale(ageInMonths, center = TRUE, scale = TRUE)[,1], 
  ) %>% 
  select(subjID, age, datacollection, symmetricPosition, targetPosition, clickDistInBalloons)

@@

write.csv(mAgeHedge, "../saves/mAgeHedge.csv", quote = F, row.names = F)
saveRDS(mAgeHedge, "../saves/mAgeHedge.rds")
```

@@

```{r age_box_model}
# define data
mDataAgeBox <- vali %>% 
  filter(studyversion == "box" & sample == "kids") %>% 
  mutate(
    # scaled (centered around mean, SD = 1, i.e., z-transformed)
    age = scale(ageInMonths, center = TRUE, scale = TRUE)[,1], 
  ) %>% 
  select(subjID, age, datacollection, symmetricPosition, targetPosition, correctBox)

@@

@@

```{r splithalfr_hedge_kids}
fn_score_hedge <- function(ds) {
  return(mean(ds$clickDistInBalloons, na.rm = TRUE))
}

@@

# first-second half split
splitscores_hedge_firstsecond_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  method = c("first_second"),
  ncores = 1,
  verbose = F
)

hedge_firstsecond_kids <- split_coefs(splitscores_hedge_firstsecond_kids, cor)
hedge_firstsecond_kids_ci <- split_ci(splitscores_hedge_firstsecond_kids, cor)

splithalf_data <- tibble(
                          sample = "kids", 
                          studyversion = "hedge", 
                          method = "first-second", 
                          stratification = "none",                                        
                          coefficient = hedge_firstsecond_kids, 
                          CI_lower = hedge_firstsecond_kids_ci$lims["0.025","bca"], 
                          CI_upper = hedge_firstsecond_kids_ci$lims["0.975","bca"]
                        )

# first-second half stratified by target position
splitscores_hedge_firstsecondStrat_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  method = c("first_second"),
  ncores = 1,
  verbose = F, 
  stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
)

hedge_firstsecondStrat_kids <- split_coefs(splitscores_hedge_firstsecondStrat_kids, cor)
hedge_firstsecondStrat_kids_ci <- split_ci(splitscores_hedge_firstsecondStrat_kids, cor)

splithalf_data <- splithalf_data %>% add_row(
                                        sample = "kids", 
                                        studyversion = "hedge", 
                                        method = "first-second",
                                        stratification = "target position",
                                        coefficient = hedge_firstsecondStrat_kids,
                                        CI_lower = hedge_firstsecondStrat_kids_ci$lims["0.025","bca"], 
                                        CI_upper = hedge_firstsecondStrat_kids_ci$lims["0.975","bca"]
                                      )

# odd-even split
splitscores_hedge_oddeven_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  method = c("odd_even"),
  ncores = 1,
  verbose = F
)

hedge_oddeven_kids <- split_coefs(splitscores_hedge_oddeven_kids, cor)
hedge_oddeven_kids_ci <- split_ci(splitscores_hedge_oddeven_kids, cor)

splithalf_data <- splithalf_data %>% add_row(
                                        sample = "kids", 
                                        studyversion = "hedge", 
                                        method = "odd-even",
                                        stratification = "none",
                                        coefficient = hedge_oddeven_kids,
                                        CI_lower = hedge_oddeven_kids_ci$lims["0.025","bca"], 
                                        CI_upper = hedge_oddeven_kids_ci$lims["0.975","bca"]
                                      )

# odd-even split stratified by target position
splitscores_hedge_oddevenStrat_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  method = c("odd_even"),
  ncores = 1,
  verbose = F, 
  stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
)

hedge_oddevenStrat_kids <- split_coefs(splitscores_hedge_oddevenStrat_kids, cor)
hedge_oddevenStrat_kids_ci <- split_ci(splitscores_hedge_oddevenStrat_kids, cor)

splithalf_data <- splithalf_data %>% add_row(
                                        sample = "kids", 
                                        studyversion = "hedge", 
                                        method = "odd-even",
                                        stratification = "target position",
                                        coefficient = hedge_oddevenStrat_kids,
                                        CI_lower = hedge_oddevenStrat_kids_ci$lims["0.025","bca"], 
                                        CI_upper = hedge_oddevenStrat_kids_ci$lims["0.975","bca"]
                                      )

# permutated splitting (random sampling without replacement)
splitscores_hedge_permutated_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  method = c("random"),
  ncores = 1,
  verbose = F, 
  replications = 1,
)

hedge_permutated_kids <- split_coefs(splitscores_hedge_permutated_kids, cor)
hedge_permutated_kids_ci <- split_ci(splitscores_hedge_permutated_kids, cor)

splithalf_data <- splithalf_data %>% add_row(
                                        sample = "kids", 
                                        studyversion = "hedge", 
                                        method = "permutated",
                                        stratification = "none",
                                        coefficient = hedge_permutated_kids,
                                        CI_lower = hedge_permutated_kids_ci$lims["0.025","bca"], 
                                        CI_upper = hedge_permutated_kids_ci$lims["0.975","bca"]
                                      )

# permutated splitting stratified by target position
splitscores_hedge_permutatedStrat_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  method = c("random"),
  ncores = 1,
  verbose = F, 
  replications = 1,
  stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
)

hedge_permutatedStrat_kids <- split_coefs(splitscores_hedge_permutatedStrat_kids, cor)
hedge_permutatedStrat_kids_ci <- split_ci(splitscores_hedge_permutatedStrat_kids, cor)

splithalf_data <- splithalf_data %>% add_row(
                                        sample = "kids", 
                                        studyversion = "hedge", 
                                        method = "permutated",
                                        stratification = "target position",
                                        coefficient = hedge_permutatedStrat_kids,
                                        CI_lower = hedge_permutatedStrat_kids_ci$lims["0.025","bca"], 
                                        CI_upper = hedge_permutatedStrat_kids_ci$lims["0.975","bca"]
                                      )

# monte carlo (sampling with replacement)
splitscores_hedge_montecarlo_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  method = c("random"),
  ncores = 1,
  verbose = F, 
  replications = 1,
  replace = TRUE,
)

hedge_montecarlo_kids <- split_coefs(splitscores_hedge_montecarlo_kids, cor)
hedge_montecarlo_kids_ci <- split_ci(splitscores_hedge_montecarlo_kids, cor)

splithalf_data <- splithalf_data %>% add_row(
                                        sample = "kids", 
                                        studyversion = "hedge", 
                                        method = "Monte Carlo",
                                        stratification = "none",
                                        coefficient = hedge_montecarlo_kids,
                                        CI_lower = hedge_montecarlo_kids_ci$lims["0.025","bca"], 
                                        CI_upper = hedge_montecarlo_kids_ci$lims["0.975","bca"]
                                      )

# monte carlo stratified by target position
splitscores_hedge_montecarloStrat_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  method = c("random"),
  ncores = 1,
  verbose = F, 
  replications = 1,
  replace = TRUE,
  stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
)

hedge_montecarloStrat_kids <- split_coefs(splitscores_hedge_montecarloStrat_kids, cor)
hedge_montecarloStrat_kids_ci <- split_ci(splitscores_hedge_montecarloStrat_kids, cor)

splithalf_data <- splithalf_data %>% add_row(
                                        sample = "kids", 
                                        studyversion = "hedge", 
                                        method = "Monte Carlo",
                                        stratification = "target position",
                                        coefficient = hedge_montecarloStrat_kids,
                                        CI_lower = hedge_montecarloStrat_kids_ci$lims["0.025","bca"], 
                                        CI_upper = hedge_montecarloStrat_kids_ci$lims["0.975","bca"]
                                      )
```

```{r splithalfr_hedge_adults}
# first-second half split
splitscores_hedge_firstsecond_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  method = c("first_second"),
  ncores = 1,
  verbose = F
)

hedge_firstsecond_adults <- split_coefs(splitscores_hedge_firstsecond_adults, cor)
hedge_firstsecond_adults_ci <- split_ci(splitscores_hedge_firstsecond_adults, cor)

splithalf_data <- splithalf_data %>% add_row(
                                              sample = "adults", 
                                              studyversion = "hedge", 
                                              method = "first-second", 
                                              stratification = "none",                                        
                                              coefficient = hedge_firstsecond_adults, 
                                              CI_lower = hedge_firstsecond_adults_ci$lims["0.025","bca"], 
                                              CI_upper = hedge_firstsecond_adults_ci$lims["0.975","bca"]
                                            )

# first-second half stratified by target position
splitscores_hedge_firstsecondStrat_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  method = c("first_second"),
  ncores = 1,
  verbose = F, 
  stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
)

hedge_firstsecondStrat_adults <- split_coefs(splitscores_hedge_firstsecondStrat_adults, cor)
hedge_firstsecondStrat_adults_ci <- split_ci(splitscores_hedge_firstsecondStrat_adults, cor)

splithalf_data <- splithalf_data %>% add_row(
                                        sample = "adults", 
                                        studyversion = "hedge", 
                                        method = "first-second",
                                        stratification = "target position",
                                        coefficient = hedge_firstsecondStrat_adults,
                                        CI_lower = hedge_firstsecondStrat_adults_ci$lims["0.025","bca"], 
                                        CI_upper = hedge_firstsecondStrat_adults_ci$lims["0.975","bca"]
                                      )

# odd-even split
splitscores_hedge_oddeven_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  method = c("odd_even"),
  ncores = 1,
  verbose = F
)

hedge_oddeven_adults <- split_coefs(splitscores_hedge_oddeven_adults, cor)
hedge_oddeven_adults_ci <- split_ci(splitscores_hedge_oddeven_adults, cor)

splithalf_data <- splithalf_data %>% add_row(
                                        sample = "adults", 
                                        studyversion = "hedge", 
                                        method = "odd-even",
                                        stratification = "none",
                                        coefficient = hedge_oddeven_adults,
                                        CI_lower = hedge_oddeven_adults_ci$lims["0.025","bca"], 
                                        CI_upper = hedge_oddeven_adults_ci$lims["0.975","bca"]
                                      )

# odd-even split stratified by target position
splitscores_hedge_oddevenStrat_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  method = c("odd_even"),
  ncores = 1,
  verbose = F, 
  stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
)

hedge_oddevenStrat_adults <- split_coefs(splitscores_hedge_oddevenStrat_adults, cor)
hedge_oddevenStrat_adults_ci <- split_ci(splitscores_hedge_oddevenStrat_adults, cor)

splithalf_data <- splithalf_data %>% add_row(
                                        sample = "adults", 
                                        studyversion = "hedge", 
                                        method = "odd-even",
                                        stratification = "target position",
                                        coefficient = hedge_oddevenStrat_adults,
                                        CI_lower = hedge_oddevenStrat_adults_ci$lims["0.025","bca"], 
                                        CI_upper = hedge_oddevenStrat_adults_ci$lims["0.975","bca"]
                                      )

# permutated splitting (random sampling without replacement)
splitscores_hedge_permutated_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  method = c("random"),
  ncores = 1,
  verbose = F, 
  replications = 1,
)

hedge_permutated_adults <- split_coefs(splitscores_hedge_permutated_adults, cor)
hedge_permutated_adults_ci <- split_ci(splitscores_hedge_permutated_adults, cor)

splithalf_data <- splithalf_data %>% add_row(
                                        sample = "adults", 
                                        studyversion = "hedge", 
                                        method = "permutated",
                                        stratification = "none",
                                        coefficient = hedge_permutated_adults,
                                        CI_lower = hedge_permutated_adults_ci$lims["0.025","bca"], 
                                        CI_upper = hedge_permutated_adults_ci$lims["0.975","bca"]
                                      )

# permutated splitting stratified by target position
splitscores_hedge_permutatedStrat_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  method = c("random"),
  ncores = 1,
  verbose = F, 
  replications = 1,
  stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
)

hedge_permutatedStrat_adults <- split_coefs(splitscores_hedge_permutatedStrat_adults, cor)
hedge_permutatedStrat_adults_ci <- split_ci(splitscores_hedge_permutatedStrat_adults, cor)

splithalf_data <- splithalf_data %>% add_row(
                                        sample = "adults", 
                                        studyversion = "hedge", 
                                        method = "permutated",
                                        stratification = "target position",
                                        coefficient = hedge_permutatedStrat_adults,
                                        CI_lower = hedge_permutatedStrat_adults_ci$lims["0.025","bca"], 
                                        CI_upper = hedge_permutatedStrat_adults_ci$lims["0.975","bca"]
                                      )

# monte carlo (sampling with replacement)
splitscores_hedge_montecarlo_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  method = c("random"),
  ncores = 1,
  verbose = F, 
  replications = 1,
  replace = TRUE,
)

hedge_montecarlo_adults <- split_coefs(splitscores_hedge_montecarlo_adults, cor)
hedge_montecarlo_adults_ci <- split_ci(splitscores_hedge_montecarlo_adults, cor)

>>>>

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse) # data handling etc.
library(viridis) # col scales, plotting...
library(ggpubr)
library(ggridges)
library(ggthemes)
library(tidyboot) # for bootstrap CIs
library(brms) # modeling
library(splithalfr) # reliability 
library(tidybayes) # for stat_halfeye
library(ggdist)
library(parallel) # for mclapply in splithalf reli

@@

```{r age_hedge_model}
mDataAgeHedge <- vali %>% 
  filter(studyversion == "hedge" & sample == "kids") %>% 
  mutate(
    # scaled (centered around mean, SD = 1, i.e., z-transformed)
    age = scale(ageInMonths, center = TRUE, scale = TRUE)[,1], 
  ) %>% 
  select(subjID, age, ageInMonths, datacollection, symmetricPosition, targetPosition, clickDistInBalloons)

@@

write.csv(mAgeHedge, "../saves/mAgeHedge.csv", quote = F, row.names = F)
saveRDS(mAgeHedge, "../saves/mAgeHedge.rds")

pp_check(mAgeHedge) + xlim(0, 10)
```

```{r GLMM_plot_hedge}
nd_hedge <- mDataAgeHedge %>% 
  select(-c(clickDistInBalloons, symmetricPosition, targetPosition))

# extract model predictions for mock data
pred_hedge <- fitted(mAgeHedge, newdata = nd_hedge, re_formula = NA) %>% as_tibble() %>% bind_cols(mDataAgeHedge)

hedge_variation_plot_GLMM <- ggplot() +

  # use model predictions for smoother
  geom_smooth(
    data = pred_hedge, 
    aes(x = ageInMonths/12, y = Estimate, ymin = Q2.5, ymax = Q97.5, group = datacollection, lty = datacollection), 
    stat = "identity", size = 0.5, alpha = 0.15, col = "darkgrey",
  ) +

  labs(x = "Age in years", y = "Average imprecision in target width", col = "Age group", shape = "Data collection mode", alpha = "Data collection mode", lty = "Data collection mode") + 
  scale_color_manual(values = c("#00b1ea", "#006c66", "#29485d", "darkgrey"), breaks = c("3", "4", "5", "18"), labels = c("3-year-olds", "4-year-olds", "5-year-olds", "Adults")) +
  scale_y_continuous(limits = c(0, 6), breaks = seq(0, 6, 1)) + 
  scale_x_continuous(breaks = seq(3, 6.5, 0.5), labels = c("3.0", "3.5", "4.0", "4.5", "5.0", "5.5", "6.0", "Adults")) +

hedge_variation_plot_GLMM

ggsave("../figures/gafo_hedge_variation_GLMM.png", width = 7, height = 4)
```

@@

```{r age_box_model}
# define data
mDataAgeBox <- vali %>% 
  filter(studyversion == "box" & sample == "kids") %>% 
  mutate(
    # scaled (centered around mean, SD = 1, i.e., z-transformed)
    age = scale(ageInMonths, center = TRUE, scale = TRUE)[,1], 
  ) %>% 
  select(subjID, age, ageInMonths, datacollection, symmetricPosition, targetPosition, correctBox)

@@

```{r GLMM_plot_box}
nd_box <- mDataAgeBox %>% 
  select(-c(correctBox, symmetricPosition, targetPosition))

# extract model predictions for mock data
pred_box <- fitted(mAgeBox, newdata = nd_box, re_formula = NA) %>% as_tibble() %>% bind_cols(mDataAgeBox)

box_variation_plot_GLMM <- ggplot() +

  # use model predictions for smoother
  geom_smooth(
    data = pred_box, 
    aes(x = ageInMonths/12, y = Estimate, ymin = Q2.5, ymax = Q97.5, group = datacollection, lty = datacollection), 
    stat = "identity", size = 0.5, alpha = 0.15, col = "darkgrey",
  ) +

box_variation_plot_GLMM

ggsave("../figures/gafo_box_variation_GLMM.png", width = 7, height = 4)
```

@@

```{r splithalfr_luke}
fn_score_hedge <- function(ds) {
  return(mean(ds$clickDistInBalloons, na.rm = TRUE))
}

@@

# random split
splitscores_hedge_random_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  replications = 25,
  method = c("random"),
  replace = TRUE,
  split_p = 1,
  ncores = 7, # setting ncores equally to something less than detectCores()
)

hedge_random_kids <- split_coefs(splitscores_hedge_random_kids, cor)
uniq_reps <- unique(splitscores_hedge_random_kids$replication)

parallel_split_ci <- function(r) {
        return(split_ci(filter(splitscores_hedge_random_kids, replication==r), cor))
}

hedge_random_kids_ci <- mclapply(uniq_reps, parallel_split_ci, mc.cores=48)
# Darn R

# create dataframe to save data
splithalf_data <- tibble(
  studyversion = "hedge",
  sample = "kids",
  split = "random",
  stratification = "none",
  mean = hedge_random_kids)

splithalf_data$CI_lower = numeric(nrow(splithalf_data))
splithalf_data$CI_upper = numeric(nrow(splithalf_data))
for(i in 1:nrow(splithalf_data)) {
  splithalf_data$CI_lower[i] <- hedge_random_kids_ci[[i]]$lims["0.025","bca"]
  splithalf_data$CI_upper[i] <- hedge_random_kids_ci[[i]]$lims["0.975","bca"]
}

print(splithalf_data)
# write_csv(splithalf_data, "splithalf_data.csv")
```

```{r splithalfr_hedge_kids}
# fn_score_hedge <- function(ds) {
#   return(mean(ds$clickDistInBalloons, na.rm = TRUE))
# }
# 
# hedge_intCon_data <- reli %>% 
#   filter(studyversion == "hedge" & reliday == "reliday1")
# 
# # first-second half split
# splitscores_hedge_firstsecond_kids <- by_split(
#   hedge_intCon_data %>% filter(sample == "kids"),
#   hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
#   fn_score_hedge,
#   method = c("first_second"),
#   ncores = 1,
#   verbose = F
# )
# 
# hedge_firstsecond_kids <- split_coefs(splitscores_hedge_firstsecond_kids, cor)
# hedge_firstsecond_kids_ci <- split_ci(splitscores_hedge_firstsecond_kids, cor)
# 
# splithalf_data <- tibble(
#                           sample = "kids", 
#                           studyversion = "hedge", 
#                           method = "first-second", 
#                           stratification = "none",                                        
#                           coefficient = hedge_firstsecond_kids, 
#                           CI_lower = hedge_firstsecond_kids_ci$lims["0.025","bca"], 
#                           CI_upper = hedge_firstsecond_kids_ci$lims["0.975","bca"]
#                         )
# 
# # first-second half stratified by target position
# splitscores_hedge_firstsecondStrat_kids <- by_split(
#   hedge_intCon_data %>% filter(sample == "kids"),
#   hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
#   fn_score_hedge,
#   method = c("first_second"),
#   ncores = 1,
#   verbose = F, 
#   stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
# )
# 
# hedge_firstsecondStrat_kids <- split_coefs(splitscores_hedge_firstsecondStrat_kids, cor)
# hedge_firstsecondStrat_kids_ci <- split_ci(splitscores_hedge_firstsecondStrat_kids, cor)
# 
# splithalf_data <- splithalf_data %>% add_row(
#                                         sample = "kids", 
#                                         studyversion = "hedge", 
#                                         method = "first-second",
#                                         stratification = "target position",
#                                         coefficient = hedge_firstsecondStrat_kids,
#                                         CI_lower = hedge_firstsecondStrat_kids_ci$lims["0.025","bca"], 
#                                         CI_upper = hedge_firstsecondStrat_kids_ci$lims["0.975","bca"]
#                                       )
# 
# # odd-even split
# splitscores_hedge_oddeven_kids <- by_split(
#   hedge_intCon_data %>% filter(sample == "kids"),
#   hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
#   fn_score_hedge,
#   method = c("odd_even"),
#   ncores = 1,
#   verbose = F
# )
# 
# hedge_oddeven_kids <- split_coefs(splitscores_hedge_oddeven_kids, cor)
# hedge_oddeven_kids_ci <- split_ci(splitscores_hedge_oddeven_kids, cor)
# 
# splithalf_data <- splithalf_data %>% add_row(
#                                         sample = "kids", 
#                                         studyversion = "hedge", 
#                                         method = "odd-even",
#                                         stratification = "none",
#                                         coefficient = hedge_oddeven_kids,
#                                         CI_lower = hedge_oddeven_kids_ci$lims["0.025","bca"], 
#                                         CI_upper = hedge_oddeven_kids_ci$lims["0.975","bca"]
#                                       )
# 
# # odd-even split stratified by target position
# splitscores_hedge_oddevenStrat_kids <- by_split(
#   hedge_intCon_data %>% filter(sample == "kids"),
#   hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
#   fn_score_hedge,
#   method = c("odd_even"),
#   ncores = 1,
#   verbose = F, 
#   stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
# )
# 
# hedge_oddevenStrat_kids <- split_coefs(splitscores_hedge_oddevenStrat_kids, cor)
# hedge_oddevenStrat_kids_ci <- split_ci(splitscores_hedge_oddevenStrat_kids, cor)
# 
# splithalf_data <- splithalf_data %>% add_row(
#                                         sample = "kids", 
#                                         studyversion = "hedge", 
#                                         method = "odd-even",
#                                         stratification = "target position",
#                                         coefficient = hedge_oddevenStrat_kids,
#                                         CI_lower = hedge_oddevenStrat_kids_ci$lims["0.025","bca"], 
#                                         CI_upper = hedge_oddevenStrat_kids_ci$lims["0.975","bca"]
#                                       )
# 
# # permutated splitting (random sampling without replacement)
# splitscores_hedge_permutated_kids <- by_split(
#   hedge_intCon_data %>% filter(sample == "kids"),
#   hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
#   fn_score_hedge,
#   method = c("random"),
#   ncores = 1,
#   verbose = F, 
#   replications = 1,
# )
# 
# hedge_permutated_kids <- split_coefs(splitscores_hedge_permutated_kids, cor)
# hedge_permutated_kids_ci <- split_ci(splitscores_hedge_permutated_kids, cor)
# 
# splithalf_data <- splithalf_data %>% add_row(
#                                         sample = "kids", 
#                                         studyversion = "hedge", 
#                                         method = "permutated",
#                                         stratification = "none",
#                                         coefficient = hedge_permutated_kids,
#                                         CI_lower = hedge_permutated_kids_ci$lims["0.025","bca"], 
#                                         CI_upper = hedge_permutated_kids_ci$lims["0.975","bca"]
#                                       )
# 
# # permutated splitting stratified by target position
# splitscores_hedge_permutatedStrat_kids <- by_split(
#   hedge_intCon_data %>% filter(sample == "kids"),
#   hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
#   fn_score_hedge,
#   method = c("random"),
#   ncores = 1,
#   verbose = F, 
#   replications = 1,
#   stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
# )
# 
# hedge_permutatedStrat_kids <- split_coefs(splitscores_hedge_permutatedStrat_kids, cor)
# hedge_permutatedStrat_kids_ci <- split_ci(splitscores_hedge_permutatedStrat_kids, cor)
# 
# splithalf_data <- splithalf_data %>% add_row(
#                                         sample = "kids", 
#                                         studyversion = "hedge", 
#                                         method = "permutated",
#                                         stratification = "target position",
#                                         coefficient = hedge_permutatedStrat_kids,
#                                         CI_lower = hedge_permutatedStrat_kids_ci$lims["0.025","bca"], 
#                                         CI_upper = hedge_permutatedStrat_kids_ci$lims["0.975","bca"]
#                                       )
# 
# # monte carlo (sampling with replacement)
# splitscores_hedge_montecarlo_kids <- by_split(
#   hedge_intCon_data %>% filter(sample == "kids"),
#   hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
#   fn_score_hedge,
#   method = c("random"),
#   ncores = 1,
#   verbose = F, 
#   replications = 1,
#   replace = TRUE,
# )
# 
# hedge_montecarlo_kids <- split_coefs(splitscores_hedge_montecarlo_kids, cor)
# hedge_montecarlo_kids_ci <- split_ci(splitscores_hedge_montecarlo_kids, cor)
# 
# splithalf_data <- splithalf_data %>% add_row(
#                                         sample = "kids", 
#                                         studyversion = "hedge", 
#                                         method = "Monte Carlo",
#                                         stratification = "none",
#                                         coefficient = hedge_montecarlo_kids,
#                                         CI_lower = hedge_montecarlo_kids_ci$lims["0.025","bca"], 
#                                         CI_upper = hedge_montecarlo_kids_ci$lims["0.975","bca"]
#                                       )
# 
# # monte carlo stratified by target position
# splitscores_hedge_montecarloStrat_kids <- by_split(
#   hedge_intCon_data %>% filter(sample == "kids"),
#   hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
#   fn_score_hedge,
#   method = c("random"),
#   ncores = 1,
#   verbose = F, 
#   replications = 1,
#   replace = TRUE,
#   stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
# )
# 
# hedge_montecarloStrat_kids <- split_coefs(splitscores_hedge_montecarloStrat_kids, cor)
# hedge_montecarloStrat_kids_ci <- split_ci(splitscores_hedge_montecarloStrat_kids, cor)
# 
# splithalf_data <- splithalf_data %>% add_row(
#                                         sample = "kids", 
#                                         studyversion = "hedge", 
#                                         method = "Monte Carlo",
#                                         stratification = "target position",
#                                         coefficient = hedge_montecarloStrat_kids,
#                                         CI_lower = hedge_montecarloStrat_kids_ci$lims["0.025","bca"], 
#                                         CI_upper = hedge_montecarloStrat_kids_ci$lims["0.975","bca"]
#                                       )
```

```{r splithalfr_hedge_adults}
# # first-second half split
# splitscores_hedge_firstsecond_adults <- by_split(
#   hedge_intCon_data %>% filter(sample == "adults"),
#   hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
#   fn_score_hedge,
#   method = c("first_second"),
#   ncores = 1,
#   verbose = F
# )
# 
# hedge_firstsecond_adults <- split_coefs(splitscores_hedge_firstsecond_adults, cor)
# hedge_firstsecond_adults_ci <- split_ci(splitscores_hedge_firstsecond_adults, cor)
# 
# splithalf_data <- splithalf_data %>% add_row(
#                                               sample = "adults", 
#                                               studyversion = "hedge", 
#                                               method = "first-second", 
#                                               stratification = "none",                                        
#                                               coefficient = hedge_firstsecond_adults, 
#                                               CI_lower = hedge_firstsecond_adults_ci$lims["0.025","bca"], 
#                                               CI_upper = hedge_firstsecond_adults_ci$lims["0.975","bca"]
#                                             )
# 
# # first-second half stratified by target position
# splitscores_hedge_firstsecondStrat_adults <- by_split(
#   hedge_intCon_data %>% filter(sample == "adults"),
#   hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
#   fn_score_hedge,
#   method = c("first_second"),
#   ncores = 1,
#   verbose = F, 
#   stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
# )
# 
# hedge_firstsecondStrat_adults <- split_coefs(splitscores_hedge_firstsecondStrat_adults, cor)
# hedge_firstsecondStrat_adults_ci <- split_ci(splitscores_hedge_firstsecondStrat_adults, cor)
# 
# splithalf_data <- splithalf_data %>% add_row(
#                                         sample = "adults", 
#                                         studyversion = "hedge", 
#                                         method = "first-second",
#                                         stratification = "target position",
#                                         coefficient = hedge_firstsecondStrat_adults,
#                                         CI_lower = hedge_firstsecondStrat_adults_ci$lims["0.025","bca"], 
#                                         CI_upper = hedge_firstsecondStrat_adults_ci$lims["0.975","bca"]
#                                       )
# 
# # odd-even split
# splitscores_hedge_oddeven_adults <- by_split(
#   hedge_intCon_data %>% filter(sample == "adults"),
#   hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
#   fn_score_hedge,
#   method = c("odd_even"),
#   ncores = 1,
#   verbose = F
# )
# 
# hedge_oddeven_adults <- split_coefs(splitscores_hedge_oddeven_adults, cor)
# hedge_oddeven_adults_ci <- split_ci(splitscores_hedge_oddeven_adults, cor)
# 
# splithalf_data <- splithalf_data %>% add_row(
#                                         sample = "adults", 
#                                         studyversion = "hedge", 
#                                         method = "odd-even",
#                                         stratification = "none",
#                                         coefficient = hedge_oddeven_adults,
#                                         CI_lower = hedge_oddeven_adults_ci$lims["0.025","bca"], 
#                                         CI_upper = hedge_oddeven_adults_ci$lims["0.975","bca"]
#                                       )
# 
# # odd-even split stratified by target position
# splitscores_hedge_oddevenStrat_adults <- by_split(
#   hedge_intCon_data %>% filter(sample == "adults"),
#   hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
#   fn_score_hedge,
#   method = c("odd_even"),
#   ncores = 1,
#   verbose = F, 
#   stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
# )
# 
# hedge_oddevenStrat_adults <- split_coefs(splitscores_hedge_oddevenStrat_adults, cor)
# hedge_oddevenStrat_adults_ci <- split_ci(splitscores_hedge_oddevenStrat_adults, cor)
# 
# splithalf_data <- splithalf_data %>% add_row(
#                                         sample = "adults", 
#                                         studyversion = "hedge", 
#                                         method = "odd-even",
#                                         stratification = "target position",
#                                         coefficient = hedge_oddevenStrat_adults,
#                                         CI_lower = hedge_oddevenStrat_adults_ci$lims["0.025","bca"], 
#                                         CI_upper = hedge_oddevenStrat_adults_ci$lims["0.975","bca"]
#                                       )
# 
# # permutated splitting (random sampling without replacement)
# splitscores_hedge_permutated_adults <- by_split(
#   hedge_intCon_data %>% filter(sample == "adults"),
#   hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
#   fn_score_hedge,
#   method = c("random"),
#   ncores = 1,
#   verbose = F, 
#   replications = 1,
# )
# 
# hedge_permutated_adults <- split_coefs(splitscores_hedge_permutated_adults, cor)
# hedge_permutated_adults_ci <- split_ci(splitscores_hedge_permutated_adults, cor)
# 
